Using traffic analysis to identify The Second Generation Onion Router

### 2011-06-11 ieee-conference-paper/paper.tex
Moving tables out into separate files and formatting widths a bit cleaner

@@

% Use the excellent biblatex package with apa style
% minnames=1,maxnames=2 - abbreviates all author names in citations
% hyperref - links in pdf
\RequirePackage[
  backend=biber,
  url = false,
  hyperref = true,
  style = ieee,
  minnames = 1,
  maxnames = 2,
  bibencoding = utf8]{biblatex}
\DeclareLanguageMapping{american}{american-apa}
\DefineBibliographyStrings{american}{% adapt language
  page = {{}p\adddot},
  pages = {{}pp\adddot},
}

@@

\begin{abstract}
Anonymous networks provide security for users by obfuscating messages with
encryption and hiding communications amongst cover traffic provided by other
network participants. The traditional goal of academic research into these
networks has been attacks that aim to uncover the identity of network users.
But the success of an anonymous network relies not only on it's technical
capabilities, but on adoption by a large enough user base to provide adequate
cover traffic. If anonymous network nodes can be identified, the users
can be harassed, discouraging participation. Tor is an example of widely used
anonymous network which uses a form of Onion Routing to provide low latency
anonymous communications. This thesis demonstrates that traffic from a simulated
Tor network can be distinguished from regular encrypted traffic, suggesting that
real world Tor users may be vulnerable to the same analysis.
\end{abstract}

@@

While Tor has been the subject of much academic literature, the primary
objective of researchers has historically been the attempt to reveal participant
identities \parencite[3]{Murdoch:2005p325}.  Many attack techniques proposed
have been somewhat academic in nature and not necessarily feasible in practice
\parencite{Raccoon:2008fk}. Sometimes they require compromise of large parts of
the Tor network, supplying hostile data to Tor users or complicated knowledge of
usage patterns and an excess of patience. The technique demonstrated in this
thesis is a low cost technique, which does not require very sophisticated
equipment and can be completed by a passive observer.

\parencite[5]{Dingledine:2004p314}.

>>>>

% For wrapping text in tables
\usepackage{array}

\usepackage[pdftex]{graphicx}
% declare the path(s) where your graphic files are
\graphicspath{{../thesis/}}

% Support for floats
\RequirePackage{float}

% For more table formatting
\RequirePackage{booktabs}

@@

% Use the excellent biblatex package with apa style
% minnames=1,maxnames=2 - abbreviates all author names in citations
% hyperref - links in pdf
\RequirePackage[
  url = false,
  hyperref = true,
  style = ieee,
  bibencoding = utf8]{biblatex}
\DeclareLanguageMapping{american}{american-apa}

@@

\begin{abstract}
Anonymous networks provide security for users by obfuscating messages with
encryption and hiding communications amongst cover traffic provided by other
network participants. The traditional goal of academic research into these
networks has been attacks that aim to uncover the identity of network users.
But the success of an anonymous network relies not only on it's technical
capabilities, but on adoption by a large enough user base to provide adequate
cover traffic. If anonymous network nodes can be identified, the users
can be harassed, discouraging participation. Tor is an example of widely used
anonymous network which uses a form of Onion Routing to provide low latency
anonymous communications. This paper demonstrates that traffic from a simulated
Tor network can be distinguished from regular encrypted traffic, suggesting that
real world Tor users may be vulnerable to the same analysis.
\end{abstract}

@@

While Tor has been the subject of much academic literature, the primary
objective of researchers has historically been the attempt to reveal participant
identities \parencite[3]{Murdoch:2005p325}.  Many attack techniques proposed
have been somewhat academic in nature and not necessarily feasible in practice
\parencite{Raccoon:2008fk}. Sometimes they require compromise of large parts of
the Tor network, supplying hostile data to Tor users or complicated knowledge of
usage patterns and an excess of patience. The technique demonstrated in this
paper is a low cost technique, which does not require very sophisticated
equipment and can be completed by a passive observer.

\section{Traffic Classification}

When considering the use of traffic analysis for classification of Internet
communications, three techniques are used. These are: exact matching, heuristic
matching and machine learning \parencite{Zhang:2009p1188}.

It is difficult to say what machine learning technique is the most effective as
no consensus has been reached, the literature covers a wide variety of
techniques each with vastly different goals and no two techniques can be
directly compared as the data used for analysis has not been disclosed
\parencite{Kim:2007p3867}. However some attempt has been made at comparison in
\textcite{Williams:2006p3849} which suggests that the C4.5 algorithm has the
greatest performance and accuracy when compared to a number of Bayesian
algorithms. \textcite{Mohd:2009p6484} compares thirty machine learning
algorithms to find random tree, IBI, IBK and random forest algorithms
obtaining the greatest classification accuracy.

\section{Experiment}

\section{Results}

The experiment was run over the course of 8 weeks yielding three sets of sample
data.

\begin{table}[H]
  \begin{tabular*}{\linewidth}{lrrr}
    \toprule
    Phase & Total Size & Packets & Sessions\\
    \midrule
    HTTPS & 9.52GB & 11,883,703 & 236,659\\
    HTTP over Tor & 10.50GB & 14,823,849 & 168,876\\
    HTTPS over Tor & 5.58GB & 8,161,620 & 95,203\\
    \bottomrule
  \end{tabular*}
  \caption{Captured Data} \label{table:datasets}
\end{table}

All of the algorithms chosen were able to successfully classify HTTPS and HTTP
over Tor traffic with accuracy in excess of 90\%, with the Adaboost algorithm
unable to classify HTTPS over Tor. The best performing algorithm random forest
was able to classify HTTP over Tor with 93.7\% accuracy and a false positive
rate of 3.7\%. HTTPS over Tor was more easily identified with a 97.7\% accuracy
and low false positive rate of 0.3\%.

\input{../thesis/weka-automated-results.tex}

When a histogram of packet sizes for each of the packet traces is produced, a
pattern becomes very apparent.

\begin{figure}[H]
  \centering\includegraphics[width=\linewidth]{https_hist}
  \caption{Histogram of packet size for HTTPS traffic}
  \label{https_hist}
\end{figure}

\begin{figure}[H]
  \centering\includegraphics[width=\linewidth]{http_tor_hist}
  \caption{Histogram of packet size for HTTP traffic over Tor}
  \label{http_tor_hist}
\end{figure}

\begin{figure}[H]
  \centering\includegraphics[width=\linewidth]{https_tor_hist}
  \caption{Histogram of packet size for HTTPS traffic over Tor}
  \label{https_tor_hist}
\end{figure}

In fact, if i

\input{../thesis/session-packet-sizes.tex}

\section{Conclusion}

Using Tor as a communications proxy incurs some overhead, sufficient enough
that when using a Tor proxy in controlled conditions, its traffic can be
distinguished from regularly encrypted traffic. This overhead may be sufficient
enough that Tor nodes in a real world network can be identified by using
readily available eavesdropping techniques.

However, this experiment was based on a small set of simulated data, with which
it would be impossible to cover all possible real world conditions. The
variability and noise present in the real Tor network may make this
classification technique impossible.

Further research needs to be conducted with live packet traces from real
participants in the Tor network. Most existing traffic classification research
operates this way, using exact matching techniques to separate traces collected
into treatment and control groups. Real Tor traffic might be captured from
publicly available and co-operating Tor nodes and compared to real encrypted
sessions between well known public HTTPS servers.

### 2011-06-11 thesis/results.tex
Moving tables out into separate files and formatting widths a bit cleaner

\begin{table}[H]
  \begin{tabular}{lrrr}
    \toprule
    & True Positive Rate & False Positive Rate & ROC Area \\
    \midrule
    Random Forest\\
    \midrule
    HTTPS & 0.957 & 0.036 & 0.99\\
    HTTP over Tor & 0.937 & 0.037 & 0.986\\
    HTTPS over Tor & 0.977 & 0.003 & 0.999\\
    Weighted Avg. & 0.954 & 0.03 & 0.99\\
    \midrule
    j4.8 With 10 fold cross validation\\
    \midrule
    HTTPS & 0.951 & 0.04 & 0.989\\
    HTTP over Tor & 0.978 & 0.043 & 0.98\\
    HTTPS over Tor & 0.97 & 0.007 & 0.992\\
    Weighted Avg. & 0.964 & 0.018 & 0.986\\
    \midrule
    Adaboost\\
    \midrule
    HTTPS & 0.95 & 0.001 & 0.975\\
    HTTP over Tor & 0.999 & 0.324 & 0.838\\
    HTTPS over Tor & 0 & 0 & 0.777\\
    Weighted Avg. & 0.785 & 0.109 & 0.891\\
    \bottomrule
  \end{tabular}
  \caption{Results}
  \label{table:results}
\end{table}

@@

Examining all of the data sets, we find the following statistics of packet
sizes:

@@

\begin{table}[H]
  \begin{tabular}{lp{14cm}}
    \toprule
    Index in Stream & Observed Packet Sizes\\
    \midrule
    HTTPS\\
    \midrule
    0 & 0\\
    1 & 0\\
    2 & 0\\
    3 & 100, 110\\
    4 & 0\\
    5 & 122, 516\\
    6 & 0\\
    7 & 6, 139\\
    8 & 0, 6, 37\\
    9 & 0, 37, 459, 465, 471, 514, 515\\
    10 & 0, 37, 417, 418, 419, 429, 436, 438, 439, 447, 448, 449, 454, 459, 463, 464, 465, 466, 470, 471, 486, 497, 499, 512, 513, 514, 523\\
    \midrule
    HTTP Over Tor\\
    \midrule
    0 & 0\\
    1 & 0\\
    2 & 0\\
    3 & 131, 132, 133, 134, 135, 136, 137, 138, 139, 140, 141, 142, 143, 144, 145, 146, 147, 148, 149, 150, 151, 152\\
    4 & 0\\
    5 & 915, 916, 917, 918, 919, 920, 921, 922, 923, 924, 925, 926, 927, 928, 929, 930, 931, 932, 933, 934\\
    6 & 0\\
    7 & 198\\
    8 & 0, 250, 266\\
    9 & 0, 250, 266, 293, 309, 325\\
    10 & 0, 293, 309, 325, 1448\\
    \midrule
    HTTPS Over Tor\\
    \midrule
    0 & 0\\
    1 & 0\\
    2 & 0\\
    3 & 131, 132, 133, 134, 135, 136, 137, 138, 139, 140, 141, 142, 144, 145, 146, 147, 148, 149, 150, 151, 152\\
    4 & 0\\
    5 & 914, 915, 916, 918, 919, 920, 921, 922, 923, 925, 926, 927, 928, 929, 930, 932, 934, 935, 936\\
    6 & 0\\
    7 & 197, 198\\
    8 & 0, 250, 266\\
    9 & 0, 250, 266, 293, 309, 325\\
    10 & 0, 293, 309, 325, 1448\\
    \bottomrule
  \end{tabular}
  \caption{Packet sizes}
  \label{table:packet_sizes}
\end{table}

>>>>

\input weka-automated-results.tex

@@

Examining all of the data sets, the following set of statistics are obtained:

@@

\input{session-packet-sizes.tex}
